---
title: "Passions"
format: html
---

## Surfing

Ever since I could stand my dad has been pushing me into waves.

## Traveling

I’ve been fortunate to spend much of my childhood—and continue to do so—traveling with family and friends. I love traveling because it allows me to explore new places, experience different cultures, and see the world from fresh perspectives. On my most recent adventure, I studied abroad in Australia. After school, seven friends and I traveled down the East Coast of Australia in a motorhome, from Brisbane to Sydney. We then flew to New Zealand, where we explored the North Island in another motorhome, chasing waves and embracing the spirit of adventure.

```{r}
# install packages individually
install.packages("here")
install.packages("tidyverse")
install.packages("DT")
install.packages("plotly")
install.packages("leaflet")
install.packages("leaflet.extras")

```

```{r}
## c. create a map!

#| eval: true
#| echo: true
# initialize map ----
site_map <- leaflet() %>% 
  
  # add base map tiles (use `addTiles()` for Google maps tiles, OR `addProviderTiles()` for 3rd party base maps: https://leaflet-extras.github.io/leaflet-providers/preview/) ----
  addProviderTiles(providers$Esri.WorldImagery, group = "ESRI World Imagery") %>% 
  addProviderTiles(providers$Esri.OceanBasemap, group = "ESRI Oceans") %>% 
  
  # add mini map ----
  addMiniMap(toggleDisplay = TRUE, minimized = TRUE) %>% 
  
  # set view over Santa Barbara Channel ----
  setView(lng =  -119.83, lat = 34.44, zoom = 9) %>% 
  
  # add MPA markers ----
  addMarkers(data = mpa, group = "MPA Sites",
             icon = lobster_icon,
             lng = ~lon, lat = ~lat,
             popup = paste("Site Name:", mpa$site, "<br>",
                           "Coordinates (lat/long):", mpa$lat, ",", mpa$lon)) %>%
  
  # add non-MPA markers ----
  addMarkers(data = non_mpa, group = "Non-MPA Sites",
             icon = lobster_icon,
             lng = ~lon, lat = ~lat,
             popup = paste("Site Name:", non_mpa$site, "<br>",
                           "Coorinates (lat/long):", non_mpa$lat, ",", non_mpa$lon)) %>%

  # add layers control (toggle base map tiles & markers based on group IDs) ----
  addLayersControl(
    baseGroups = c("ESRI World Imagery", "ESRI Oceans"),
    overlayGroups = c("MPA Sites", "Non-MPA Sites")) %>% 
  
  # add reset map button ----
  leaflet.extras::addResetMapButton()

# print map ----
site_map

```

```{r}
#| eval: false
#| echo: true
htmltools::save_html(lobs_interactive, here::here("outputs", "plotly.html"))
htmltools::save_html(lobs_dt, here::here("outputs", "dt.html"))
htmltools::save_html(site_map, here::here("outputs", "leaflet.html"))
```
